\documentclass{article}[12pt]

\begin{document}

\title{Design of the ReWire Haskell-to-Hardware Compiler}
\author{Adam Procter}

\maketitle

\section{Introduction}\label{section:introduction}

What is ReWire?

How is this document structured?

\section{Mapping Resumptions to Hardware}

How do resumptions map to (clocked, sequential) hardware circuits?

Well, first of all, what's a reactive resumption? Assume WLOG that it never gets ``done'': then you are talking about a machine that maps a sequence (discrete-time) of inputs to a sequence of outputs. That's just a sequential circuit. (Diagram.)

Now, consider this module

\begin{verbatim}
module Foo where
...
main :: React I O ()
\end{verbatim}

this is gonna look like

\begin{verbatim}
entity Foo is
  port (clk  : in std_logic;                           -- clock signal, always present
        inp  : in std_logic_vector ([|I|] downto 0);   -- input signal (absent if I isomorphic to ()).
        outp : out std_logic_vector ([|O|] downto 0)); -- output signal if present (absent if O isomorphic to ()).
end Foo;
\end{verbatim}

(Thought: it might be better to have a ``done-less'' react-ish type, i.e. the automata arrow, as the base, but it doesn't matter much.)

\section{Compiler Structure}

Broken into syntax modules (AST with utility functions) and compiler modules (each with a ``pure'' interface though they may be monadic internally) transforming syntax to syntax.

Block diagram here like what was on the white board. Each module will correspond to a single Haskell module.

\subsection{Syntax Modules}

GHC's Haskell AST (wherever that comes from), RWC, SMIL.

\subsection{Compiler Modules}

\section{ReWire Core}

\section{Desugarer}

This translates type-checked GHC modules into ReWire Core.

\section{ReWire Normal Form}

RWNF for short.

\section{Partial Evaluator}

This tries to map type-checked GHC modules with ``main'' of acceptable type down to RWNF.

\section{State Machine Generator}

\section{VHDL Generator}

\appendix

\section{Abstract Syntax Reference}

\subsection{ReWire Core}

\subsection{SMIL}

\end{document}